\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{charter}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}
\setlength{\footskip}{3.60004pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\vspace{-10pt}\rule{\textwidth}{0.5pt}\vspace{-5pt}]
\titlespacing*{\section}{0pt}{12pt}{4pt}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=1.5pt, parsep=0pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Teng Wen Kee} \\ \vspace{6pt}
    \small \href{mailto:wenwork4140@gmail.com}{wenwork4140@gmail.com} $|$ \href{https://www.linkedin.com/in/teng-wen-kee}{linkedin.com/in/teng-wen-kee} $|$ \href{https://github.com/AmIWhatIAm}{github.com/AmIWhatIAm}
\end{center}

%----------EDUCATION----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universiti Tunku Abdul Rahman (UTAR)}{Kajang, Selangor}
      {Bachelor of Software Engineering (Honours) -- Distinction / First Class}{Jun 2023 -- Jun 2026}
      \resumeItemListStart
        \resumeItem{Cumulative Grade Point Average (CGPA) of \textbf{3.8115 / 4.0}}
        \resumeItem{Achieved President's Lists (x2) and Dean's Lists (x5)}
        \resumeItem{Awarded and maintained \textbf{100\% UTAR Top Achiever Scholarship}}
        \resumeItem{Scored Malaysian University English Test (MUET) with \textbf{Band 4.5}}
      \resumeItemListEnd
      
    \resumeSubheading
      {Universiti Tunku Abdul Rahman (UTAR)}{Kajang, Selangor}
      {Foundation in Science -- Physical Science (Technological Science)}{Jun 2022 -- May 2023}
      \resumeItemListStart
        \resumeItem{Scored CGPA of \textbf{3.96 / 4.0}}
        \resumeItem{Achieved President's Lists (x3)}
        \resumeItem{Awarded and maintained \textbf{50\% UTAR Top Achiever Scholarship}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------EXPERIENCE----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Agmo Artisan Sdn. Bhd.}{Kuala Lumpur, Federal Territory of Kuala Lumpur}
      {Frontend Web Developer Intern}{Oct 2025 -- Jan 2026}
      \resumeItemListStart
        \resumeItem{Leveraged \textbf{Agile/Scrum} methodologies to resolve \textbf{15+ high-priority Jira tickets} within 2 months, successfully shipping frontend sub-features and debugging issues.}
        \resumeItem{Translated complex Figma designs into \textbf{responsive, pixel-perfect web components} using \textbf{Next.js and Tailwind CSS}, ensuring cross-platform UI consistency and optimal user experience.}
        \resumeItem{Engineered custom \textbf{Selenium automation scripts} to streamline repetitive tasks, while contributing to \textbf{Laravel} backend codebases to accelerate project delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {Treehole Story Enterprise}{Remote}
      {Freelance Frontend Web Developer}{Jan 2025 -- Feb 2025}
      \resumeItemListStart
        \resumeItem{Developed interactive and responsive UI sections from designer mockups using \textbf{Next.js} and \textbf{Tailwind CSS}, optimizing for seamless desktop and mobile viewports.}
        \resumeItem{Identified and resolved rendering bugs and layout discrepancies, reducing visual inconsistency across devices.}
        \resumeItem{Implemented fluid custom web animations to elevate platform aesthetics.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Acadia -- Fullstack Web \& Mobile Augmented Reality (AR) Digital Solution (Final Year Project)}}{}
          \resumeItemListStart
            \resumeItem{Architected a full-stack, cross-platform ecosystem bridging a \textbf{Nuxt.js (Vue.js)} web application with a Unity mobile companion app, using \textbf{PostgreSQL via Supabase} for centralized data management.}
            \resumeItem{Engineered real-time data pipelines allowing a mobile AR app built with \textbf{Unity (C\#)} and \textbf{Vuforia Engine} to dynamically stream and manipulate 3D visual assets on the desktop web interface.}
            \resumeItem{Designed relational data models to securely manage user authentication, session management, and synchronized states.}
            \resumeItem{\textit{Repositories:} \href{https://github.com/AmIWhatIAm/acadia-web}{github.com/AmIWhatIAm/acadia-web} | \href{https://github.com/AmIWhatIAm/acadia-ar-companion}{github.com/AmIWhatIAm/acadia-ar-companion}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Frontend Web:} Next.js, React.js, Nuxt.js, Vue.js, Tailwind CSS, Shadcn/ui, HTML5/CSS3 \\
     \textbf{Backend \& APIs:} Node.js, Laravel (PHP), RESTful APIs \\
     \textbf{Languages:} TypeScript, JavaScript, PHP, Python, SQL, C\# (Unity) \\
     \textbf{Databases \& Cloud:} Supabase, MySQL, PostgreSQL, Relational Data Modeling \\
     \textbf{Developer Tools \& Automation:} Git, GitHub, GitLab, Claude Code, VS Code, Vuforia Engine, Selenium (Browser Automation) \\
     \textbf{Productivity \& Project Management:} Jira (Agile/Scrum), Figma, Axure RP, Trello, Notion, MS Project
    }}
 \end{itemize}

%-----------LEADERSHIP & EXTRACURRICULARS-----------
\section{Extracurriculars \& Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Malaysian Board of Technologists (MBOT) Student Chapter}{}
      {Auditor (2025 -- 2026) | Assistant Secretary (2024 -- 2025)}{Jun 2024 -- Jun 2026}
      \resumeItemListStart
        \resumeItem{Directed operational workflows and audited administrative documentation for a professional student tech chapter, scaling member engagement through high-impact tech events.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{Volunteering \& Certifications}}{}
      \resumeItemListStart
        \resumeItem{Achieved UTAR's highest \textbf{Platinum Grade for Soft Skills \& Leadership} and a \textbf{5-Star Rating for Community Service} across 140+ hours of voluntary initiatives.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}